Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-07-15 draft/draft.tex
progress

\item 
Compute ratings defining the $f_{ij}=\phi_j-\phi_i$ where the strength $\phi_i = \sum_j w_{ij}$ defines a local potential for the $i$-th team.
\end{enumerate}

>>>>

\item 
Compute ratings defining the 1-cochain coordiantes $f'_{ij}=\phi_j-\phi_i$, where the strength $\phi_i = \sum_j w_{ij}$ defines a local potential for the $i$-th team.
\end{enumerate}
